Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-01-09 tex/test-WW-type-00s-PS.tex
alexei

In the structure function $F_{UT}^{\sin\phi_S}$ we encounter 3 interesting 
new features. This is the first case with more than 1 contribution after 
applying the WW-type approximation. Assuming Gauss Ans\"atze for the TMDs
$f_T^q(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
we obtain 
\begin{subequations}\begin{alignat}{1}
	F_{UT}^{\sin\phi_S}(x,z,\Phperp) 
	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	  x\,f_T^q(x)
	\, D_1(z) \, { \cal G}(\Phperp)  \label{Eq:FUTsinphiS-Gauss-I-PhT}\\
	&- {\textstyle\frac12}\,x\,\left(h_T^{(1)q}(x)-h_T^{\perp(1)q}(x)\right)
	\,H_1^{\perp(1)q}(z)\; \frac{4z^2 m_h\,M_N}{\lambda} 
	\left(1-\frac{\Phperp^2}{\lambda}\right) {\cal G}(\Phperp) \Biggr] 
  	\nonumber\\
	F_{UT}^{\sin\phi_S}(x,z) 
	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\, x\,f_T^q(x)\, D_1(z) 
	\label{Eq:FUTsinphiS-I-naive}\
\end{alignat}\end{subequations}
with  respectively
$\lambda=z^2\la\kperp^2\ra_{f_T}+\la\pperp^2\ra_{D_1}$ in the first, and  
$\lambda=z^2\la\kperp^2\ra_{h_T^\perp}+\la\pperp^2\ra_{H_1^\perp}$ in the 
second term of Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}) where we 
assumed $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}$.

@@

The asymmetries $A_{UT}^{\sin\phi_S}=F_{UT}^{\sin\phi_S}/F_{UU}$  for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{autsinphi_jlab}.
\PS{Compare to HERMES data \cite{Schnell:2010zza}?
Is there by now final data? Will be interesting!}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphi_PT.pdf}
\caption{\label{autsinphi_jlab} $A_{UT}^{\sin\phi_S}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The structure function $F_{UU}^{\cos\phi_h}$, Eq.~(\ref{Eq:FUUcosphi}),
contains after the WW-type approximation two contributions. Assuming
Gaussian Ans\"atze for $h^{q}(x,\kperp)$ and $f^\perp(x,\pperp)$ we obtain
\begin{subequations}\begin{alignat}{1}
	F_{UU}^{\cos\phi_h}(x,z,\Phperp) 
	= \red{+}\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;b^{(1)}_{\rm A}\,
	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, & { \cal G}(\Phperp)
	  \nonumber\\
	\red{-} x\,f^{\perp(1)q}(x)\,D_1^q(z)\;b^{(1)}_{\rm B}\,
	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, & { \cal G}(\Phperp ) 
	\Biggr] \label{Eq:XXXa}\\
	F_{UU}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
	= \red{+}\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;c^{(1)}_{\rm A}\;
	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)&
	  \nonumber\\
	\red{-}x\,f^{\perp(1)q}(x)\,D_1^q(z)\;c^{(1)}_{\rm B}\;
	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)&
	\Biggr] \label{Eq:XXXb}
\end{alignat}\end{subequations}
with $\lambda=z^2\la\kperp^2\ra_{h}+\la\pperp^2\ra_{H_1^\perp}$ in the first, 
and  $\lambda=z^2\la\kperp^2\ra_{f^\perp}+\la\pperp^2\ra_{D_1}$ in the second 
term respectively in (\ref{Eq:XXXa}) and (\ref{Eq:XXXb}). The coefficients 
$b^{(1)}_i$ and $c^{(1)}_i$ are defined in App.~\ref{App:convol-details}.

@@

For $f^{\perp(1)}(x)$ we explore Eq.~(\ref{Eq:WW-type-Cahn}) as
\be
	x\,f^{\perp(1)}(x) = \frac{\la\kperp^2\ra_{f_1}}{2M_N^2}\,f_{1}^q(x)
	\, , 
\ee\end{subequations}
and estimate its Gaussian width as $\la\kperp^2\ra_{f^\perp}=\la\kperp^2\ra_{f_1}$.
The latter means the Gaussian factors of 
$F_{UU}^{\cos\phi_h}$ and $F_{UU}$ cancel out, i.e.\ at some point 
for $\Phperp\gtrsim1\,$GeV we would obtain from (\ref{Eq:XXXa}) 
an asymmetry $A_{UU}^{\cos\phi_h}=F_{UU}^{\cos\phi_h}/F_{UU}$ exceeding
100$\,\%$ and violating unitarity. This is of course an artifact of our 
approximations, and reminds us that the WW-type approximations as well
as the entire TMD formalism must be applied to small $\Phperp\ll Q$,
and in the case of $A_{UU}^{\cos\phi_h}$ preferably for $\Phperp < 1\,$GeV,
as shown in Fig.~\ref{auucosphi_jlab}. \\
\PS{(Alexei: did you notice it \cite{Anselmino:2005nn}? How did you treat it?)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_PT.pdf}
\caption{\label{auucosphi_jlab} $A_{UU}^{\cos\phi_h}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%------ BEGIN FIGURE 4: Phperp(z) AND Phperp^2(z) at HERMES ----------
        \begin{figure}[b!]
        \vspace{-0.6cm}
        \includegraphics[height=8cm]{\FigPath/Fig06-EMC-cosphi-z.pdf}
        \vspace{-0.5cm}
        \caption{\label{Fig-02:EMC}
        Azimuthal asymmetry $A_{UU}^{\cos\phi}$ in charged hadron 
        production in SIDIS of $280\,{\rm GeV}$ muons off protons
        as function of $z$. The data from EMC \cite{Aubert:1983cz}
        refer to $\la Q\ra=4.8\,{\rm GeV}$. The theoretical
        curve is the ``WW-type and Cahn-effect-only'' approximation 
        for this observable in the Gauss model with parameters 
        fixed from HERMES data and neglecting evolution effects. 
	From Ref.~\cite{Schweitzer:2010tt}.}
        \end{figure}
%------ END FIGURE 4 -------------------------------------------------

@@

In this last asymmetry we encounter the first case with more than 
1 contribution in our treatment. Assuming Gauss Ans\"atze for 
$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ we find
\begin{subequations}\begin{alignat}{1}
	F_{UT}^{\sin(2\phi_h -\phi_S)}(x,z,\Phperp) \; \; 
	= \; \; \; \;
	\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	x \; f_T^{\perp(2)q}(x) \; D_1(z) \;b^{(2)}_{\rm C}\;
	&\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\;{ \cal G}(\Phperp) 
	\nonumber\\
	+ \;
	x\left(h_T^{(1)q}(x)+h_T^{\perp(1)q}(x)\right)H_1^{\perp(1)q}(z)\,
	\frac{b^{(2)}_{\rm AB}}{2}
	&\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\;{\cal G}(\Phperp)\Biggr] 
	\label{Eq:FUTsin2phi-phiS-Gauss-PhT}\\
{ }
	F_{UT}^{\sin(2\phi_h -\phi_S)}(x,z,\Phperp) \; \; 
	= \; \; \; \;
	\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	x \; f_T^{\perp(2)q}(x) \; D_1(z) \; c^{(2)}_{\rm C} \;
	&\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2}
	\nonumber\\
	+ \;
	x\left(h_T^{(1)q}(x)+h_T^{\perp(1)q}(x)\right)H_1^{\perp(1)q}(z)\,
	\frac{c^{(2)}_{\rm AB}}{2}
	&\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2}\Biggr] 
	\label{Eq:FUTsin2phi-phiS-Gauss}
\end{alignat}\end{subequations}
with respectively 
$\lambda=z^2\la\kperp^2\ra_{f_T^\perp}+\la\pperp^2\ra_{D_1}$ in the first, and  
$\lambda=z^2\la\kperp^2\ra_{h_T^\perp}+\la\pperp^2\ra_{H_1^\perp}$ in the second 
terms in 
Eqs.~(\ref{Eq:FUTsin2phi-phiS-Gauss-PhT},~\ref{Eq:FUTsin2phi-phiS-Gauss}).
We use $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T}$. The coefficients 
$b^{(2)}_i$ and $c^{(2)}_i$ are defined in App.~\ref{App:convol-details}.
We now explore the WW-type approximations in
Eqs.~(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}) to 
express the twist-3 TMDs in terms of the Sivers function and pretzelosity
as follows
\begin{subequations}\ba
   	x \, f_T^{\perp(2)q}(x) 
	&=& f_{1T}^{\perp (2)q}(x) 
	\equiv \frac{\la\kperp^2\ra_{f_{1T}^\perp}}{M_N^2}\,f_{1T}^{\perp (1)q}(x)\,,\\
   	-\,{\textstyle\frac12}\,x \left(h_T^{(1)q}(x) + h_T^{\perp(1)q}(x)\right)
	&=& h_{1T}^{\perp(2)q}(x) \, .
%	\equiv\frac{\la\kperp^2\ra_{f_{1T}^\perp}}{M_N^2}\,f_{1T}^{\perp(1)q}(x)
\ea\end{subequations}
%
%
% $xh_T^q(x,\kperp^2)        =-h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2)$
% $xh_T^{\perp q}(x,\kperp^2)= h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2)$
%
% $xf_T^{\perp q}(x,\kperp^2) = f_{1T}^{\perp   q}(x,\kperp^2)$
% $xf_T^{q}      (x,\kperp^2) =-f_{1T}^{\perp(1)q}(x,\kperp^2)$
%
% In our approach this is the only asymmetry which receives 2 contributions.
The asymmetries $A_{UT}^{\sin (2 \phi_h-\phi_S)}=F_{UT}^{\sin (2 \phi_h-\phi_S)}/F_{UU}$  
for Jefferson Lab 12 GeV are plotted in Fig.~\ref{autsin2phi_jlab}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2phi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2phi_PT.pdf}
\caption{\label{autsin2phi_jlab} $A_{UT}^{\sin(2\phi_h- \phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{\boldmath Unpolarised functions $f_1^a(x,k_\perp)$ 
			and $D_1(z,P_\perp)$}
\label{App:basis-f1-D1}

@@

To describe the transverse momentum dependence of $f_1^a(x,k_\perp)$ 
and $D_1(z,P_\perp)$ we use the Gaussian Ansatz in 
Eqs.~(\ref{Eq:Gauss-f1-D1}). All early 
\cite{Anselmino:2005nn,Collins:2005ie,D'Alesio:2007jt,Schweitzer:2010tt}
and some recent \cite{Signori:2013mda} analyses employed flavor and 
$x$- or $z$-independent widths $\avkperp$ and $\avpperp$.
In the the analysis \cite{Anselmino:2013lza} 
of HERMES multiplicities flavor-independence of the widths was 
assumed. On long run one may anticipate that new precision data will 
require to relax these assumptions. However, one may also expect that the 
Gaussian Ansatz will remain a useful {\it approximation} as long as one is 
interested in describing data on transverse hadron momenta $\Phperp \ll Q $.

@@

\subsection{\boldmath Helicity distribution $g_1^a(x,k_\perp)$}
\label{App:basis-g1}

For the helicity PDF $g_1^a(x)=\int d^2k_\perp\,g_1^a(x,k_\perp)\equiv 
\int d^2k_\perp\,g_{1L}^a(x,k_\perp)$ we use in this work the leading-order 
parameterizations from \cite{Gluck:1998xa}.
If not otherwise stated the parametrizations are taken at the scale 
$Q^2=2.5\,{\rm GeV}^2$.

In lack of phenomenological information on the $k_\perp$-dependence of
$g_1^a(x,k_\perp)$ we explore lattice QCD results from \cite{Hagler:2009mb}
to constrain the Gaussian width in Eq.~(\ref{eq:g1}). 
On a lattice with pion and nucleon masses 
$m_\pi\approx 500\,{\rm MeV}$ and $M_N=1.291(23)\,{\rm GeV}$ 
and with an axial coupling constant $g_A^{(3)}= 1.209(36)$ reasonably
close to its physical value $1.2695(29)$ the following results were
obtained for the mean square transverse parton momenta \cite{Hagler:2009mb}.
For the unpolarized TMDs it was found
$\langle \kperp^2 \rangle_{f_1^u} = (0.3741\,{\rm GeV})^2$ and
$\langle \kperp^2 \rangle_{f_1^d} = (0.3839\,{\rm GeV})^2$.
For the helicity TMDs it was found
$\avkperp_{g_1^u} = (0.327\,{\rm GeV})^2$ and
$\avkperp_{g_1^d} = (0.385\,{\rm GeV})^2$. 
These values are quoted in Table~\ref{Table:Gauss-paramaters}.

@@

\ba
f_{1T}^{\perp q}(x,\kperp) =  f_{1T}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{f_{1T}^\perp}^2} e^{-\kperp^2/{\avkperp_{f_{1T}^\perp}}}
\label{sivers_new} \ .
\ea

@@

\newpage
\section{Convolution integrals and expressions in Gaussian Ansatz}}
\label{App:factor}

>>>>

In the structure function $F_{UT}^{\sin\phi_S}$ we encounter 3 interesting 
new features. This is the first case with more than 1 contribution after 
applying the WW-type approximation. Assuming Gauss Ans\"atze for the TMDs
$f_T^q(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
\begin{subequations}
\be
f_T^q(x,\kperp^2) = f_T^q(x) \,\frac{1}{\pi \avkperp_{f_{T}}}\,
	e^{-\kperp^2/{\avkperp_{f_{T}}}}\;,
	\label{eq:fTnew}
\ee
\be
h_T^{\perp q}(x,\kperp^2) =h_T^{\perp (1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{h_{T}^\perp}^2}\,
	e^{-\kperp^2/{\avkperp_{h_{T}^\perp}}}\;,
	\label{eq:hTperpnew}
\ee
\be
h_T^{q}(x,\kperp^2) =h_T^{(1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{h_{T}}^2}\,
	e^{-\kperp^2/{\avkperp_{h_{T}}}}\;,
	\label{eq:hTnew}
\ee
\end{subequations}
we obtain 
\begin{subequations}\begin{alignat}{1}
	F_{UT}^{\sin\phi_S}(x,z,\Phperp) 
	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	  x\,f_T^q(x)
	\, D_1(z) \, { \cal G}(\Phperp)  \label{Eq:FUTsinphiS-Gauss-I-PhT}\\
	&- {\textstyle\frac12}\,x\,\left(h_T^{(1)q}(x)-h_T^{\perp(1)q}(x)\right)
	\,H_1^{\perp(1)q}(z)\; \frac{4z^2 m_h\,M_N}{\lambda} 
	\left(1-\frac{\Phperp^2}{\lambda}\right) {\cal G}(\Phperp) \Biggr] 
  	\nonumber\\
	F_{UT}^{\sin\phi_S}(x,z) 
	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\, x\,f_T^q(x)\, D_1(z) 
	\label{Eq:FUTsinphiS-I-naive}\
\end{alignat}\end{subequations}
with  respectively
$\lambda=z^2\la\kperp^2\ra_{f_T}+\la\pperp^2\ra_{D_1}$ in the first, and  
$\lambda=z^2\la\kperp^2\ra_{h_T^\perp}+\la\pperp^2\ra_{H_1^\perp}$ in the 
second term of Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}) where we 
assumed $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}$.

@@

The asymmetries $A_{UT}^{\sin\phi_S}=F_{UT}^{\sin\phi_S}/F_{UU}$  for 
COMPASS are plotted in Fig.~\ref{autsinphi_jlab}.
\PS{Compare to HERMES data \cite{Schnell:2010zza}?
Is there by now final data? Will be interesting!}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphiS_COMPASS_x.pdf} 
\caption{\label{autsinphi_jlab} $A_{UT}^{\sin\phi_S}$  as a function of $ x $ for COMPASS.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The structure function $F_{UU}^{\cos\phi_h}$, Eq.~(\ref{Eq:FUUcosphi}),
contains after the WW-type approximation two contributions. Assuming
Gaussian Ans\"atze for $h^{q}(x,\kperp)$ and $f^\perp(x,\pperp)$ 
\begin{subequations}
\be
h^q(x,\kperp^2) = h^q(x) \,\frac{1}{\pi \avkperp_{h}}\,
	e^{-\kperp^2/{\avkperp_{h}}}\;,
	\label{eq:hnew}
\ee
\be
f^{\perp q}(x,\kperp^2) =f^{\perp (1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{f^\perp}^2}\,
	e^{-\kperp^2/{\avkperp_{f^\perp}}}\;,
	\label{eq:fperpnew}
\ee
\end{subequations}
we obtain
\begin{subequations}\begin{alignat}{1}
	F_{UU}^{\cos\phi_h}(x,z,\Phperp) 
	= +\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;b^{(1)}_{\rm A}\,
	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, & { \cal G}(\Phperp)
	  \nonumber\\
	- x\,f^{\perp(1)q}(x)\,D_1^q(z)\;b^{(1)}_{\rm B}\,
	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, & { \cal G}(\Phperp ) 
	\Biggr] \label{Eq:XXXa}\\
	F_{UU}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
	= +\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;c^{(1)}_{\rm A}\;
	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)&
	  \nonumber\\
	-x\,f^{\perp(1)q}(x)\,D_1^q(z)\;c^{(1)}_{\rm B}\;
	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)&
	\Biggr] \label{Eq:XXXb}
\end{alignat}\end{subequations}
with $\lambda=z^2\la\kperp^2\ra_{h}+\la\pperp^2\ra_{H_1^\perp}$ in the first, 
and  $\lambda=z^2\la\kperp^2\ra_{f^\perp}+\la\pperp^2\ra_{D_1}$ in the second 
term respectively in (\ref{Eq:XXXa}) and (\ref{Eq:XXXb}). The coefficients 
$b^{(1)}_i$ and $c^{(1)}_i$ are defined in App.~\ref{App:convol-details}.

@@

For $f^{\perp(1)}(x)$ we explore Eq.~(\ref{Eq:WW-type-Cahn}) as
\be
	x\,f^{\perp(1)}(x) = \frac{\la\kperp^2\ra_{f_1}}{2M_N^2}\,f_{1}^q(x)
	\, , 
\ee\end{subequations}
and estimate its Gaussian width as $\la\kperp^2\ra_{f^\perp}=\la\kperp^2\ra_{f_1}$.
The latter means the Gaussian factors of 
$F_{UU}^{\cos\phi_h}$ and $F_{UU}$ cancel out, i.e.\ at some point 
for $\Phperp\gtrsim1\,$GeV we would obtain from (\ref{Eq:XXXa}) 
an asymmetry $A_{UU}^{\cos\phi_h}=F_{UU}^{\cos\phi_h}/F_{UU}$ exceeding
100$\,\%$ and violating unitarity. This is of course an artifact of our 
approximations, and reminds us that the WW-type approximations as well
as the entire TMD formalism must be applied to small $\Phperp\ll Q$,
and in the case of $A_{UU}^{\cos\phi_h}$ preferably for $\Phperp < 1\,$GeV,
as shown in Fig.~\ref{auucosphi_jlab}. \\
\PS{(Alexei: did you notice it \cite{Anselmino:2005nn}? How did you treat it? AP we did notice and did nothing.)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_PT.pdf} 
\caption{\label{auucosphi_jlab} $A_{UU}^{\cos\phi_h}$  for COMPASS.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%------ BEGIN FIGURE 4: Phperp(z) AND Phperp^2(z) at HERMES ----------
        \begin{figure}[b!]
        \vspace{-0.6cm}
        \includegraphics[height=8cm]{\FigPath/Fig06-EMC-cosphi-z.pdf}
        \vspace{-0.5cm}
        \caption{\label{Fig-02:EMC}
        Azimuthal asymmetry $A_{UU}^{\cos\phi}$ in charged hadron 
        production in SIDIS of $280\,{\rm GeV}$ muons off protons
        as function of $z$. The data from EMC \cite{Aubert:1983cz}
        refer to $\la Q\ra=4.8\,{\rm GeV}$. The theoretical
        curve is the ``WW-type and Cahn-effect-only'' approximation 
        for this observable in the Gauss model with parameters 
        fixed from HERMES data and neglecting evolution effects. 
	From Ref.~\cite{Schweitzer:2010tt}.}
        \end{figure}
%------ END FIGURE 4 -------------------------------------------------

@@

@@

In this last asymmetry we encounter the first case with more than 
1 contribution in our treatment. Assuming Gauss Ans\"atze for 
$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$ (Eq.~\ref{eq:hTperpnew}), $h_T^q(x,\kperp)$ (Eq.~\ref{eq:hTnew}),
\be
	f^{\perp q}_{T}(x,\kperp^2) = 
	f^{\perp (2) q}_{T}(x)\,\frac{2 M^4}{\pi \avkperp^3_{f_{T}^{\perp} }}\,
	e^{-\kperp^2/{\avkperp_{f_{T}^{\perp} }}}\;,
	\label{eq:ftperpnew}
\ee
we find
\begin{subequations}\begin{alignat}{1}
	F_{UT}^{\sin(2\phi_h -\phi_S)}(x,z,\Phperp) \; \; 
	= \; \; \; \;
	\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	x \; f_T^{\perp(2)q}(x) \; D_1(z) \;b^{(2)}_{\rm C}\;
	&\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\;{ \cal G}(\Phperp) 
	\nonumber\\
	+ \;
	x\left(h_T^{(1)q}(x)+h_T^{\perp(1)q}(x)\right)H_1^{\perp(1)q}(z)\,
	\frac{b^{(2)}_{\rm AB}}{2}
	&\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\;{\cal G}(\Phperp)\Biggr] 
	\label{Eq:FUTsin2phi-phiS-Gauss-PhT}\\
{ }
	F_{UT}^{\sin(2\phi_h -\phi_S)}(x,z,\Phperp) \; \; 
	= \; \; \; \;
	\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	x \; f_T^{\perp(2)q}(x) \; D_1(z) \; c^{(2)}_{\rm C} \;
	&\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2}
	\nonumber\\
	+ \;
	x\left(h_T^{(1)q}(x)+h_T^{\perp(1)q}(x)\right)H_1^{\perp(1)q}(z)\,
	\frac{c^{(2)}_{\rm AB}}{2}
	&\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2}\Biggr] 
	\label{Eq:FUTsin2phi-phiS-Gauss}
\end{alignat}\end{subequations}
with respectively 
$\lambda=z^2\la\kperp^2\ra_{f_T^\perp}+\la\pperp^2\ra_{D_1}$ in the first, and  
$\lambda=z^2\la\kperp^2\ra_{h_T^\perp}+\la\pperp^2\ra_{H_1^\perp}$ in the second 
terms in 
Eqs.~(\ref{Eq:FUTsin2phi-phiS-Gauss-PhT},~\ref{Eq:FUTsin2phi-phiS-Gauss}).
We use $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T}$. The coefficients 
$b^{(2)}_i$ and $c^{(2)}_i$ are defined in App.~\ref{App:convol-details}.
We now explore the WW-type approximations in
Eqs.~(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}) to 
express the twist-3 TMDs in terms of the Sivers function and pretzelosity
as follows
\begin{subequations}\ba
   	x \, f_T^{\perp(2)q}(x) 
	&=& f_{1T}^{\perp (2)q}(x) 
	\equiv \frac{\la\kperp^2\ra_{f_{1T}^\perp}}{M_N^2}\,f_{1T}^{\perp (1)q}(x)\,,\\
   	-\,{\textstyle\frac12}\,x \left(h_T^{(1)q}(x) + h_T^{\perp(1)q}(x)\right)
	&=& h_{1T}^{\perp(2)q}(x) \, .
%	\equiv\frac{\la\kperp^2\ra_{f_{1T}^\perp}}{M_N^2}\,f_{1T}^{\perp(1)q}(x)
\ea\end{subequations}
%
%
% $xh_T^q(x,\kperp^2)        =-h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2)$
% $xh_T^{\perp q}(x,\kperp^2)= h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2)$
%
% $xf_T^{\perp q}(x,\kperp^2) = f_{1T}^{\perp   q}(x,\kperp^2)$
% $xf_T^{q}      (x,\kperp^2) =-f_{1T}^{\perp(1)q}(x,\kperp^2)$
%
% In our approach this is the only asymmetry which receives 2 contributions.
The asymmetries $A_{UT}^{\sin (2 \phi_h-\phi_S)}=F_{UT}^{\sin (2 \phi_h-\phi_S)}/F_{UU}$  
for Jefferson Lab 12 GeV are plotted in Fig.~\ref{autsin2phi_jlab}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x.pdf} 
\caption{\label{autsin2phi_jlab} $A_{UT}^{\sin(2\phi_h- \phi_S)}$  for COMPASS.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{\boldmath Unpolarised functions $f_1^a(x,k_\perp^2)$ 
			and $D_1(z,P_\perp^2)$}
\label{App:basis-f1-D1}

@@

To describe the transverse momentum dependence of $f_1^a(x,k_\perp^2)$ 
and $D_1(z,P_\perp^2)$ we use the Gaussian Ansatz in 
Eqs.~(\ref{Eq:Gauss-f1-D1}). All early 
\cite{Anselmino:2005nn,Collins:2005ie,D'Alesio:2007jt,Schweitzer:2010tt}
and some recent \cite{Signori:2013mda} analyses employed flavor and 
$x$- or $z$-independent widths $\avkperp$ and $\avpperp$.
In the the analysis \cite{Anselmino:2013lza} 
of HERMES multiplicities flavor-independence of the widths was 
assumed. On long run one may anticipate that new precision data will 
require to relax these assumptions. However, one may also expect that the 
Gaussian Ansatz will remain a useful {\it approximation} as long as one is 
interested in describing data on transverse hadron momenta $\Phperp \ll Q $.

@@

\subsection{\boldmath Helicity distribution $g_1^a(x,k_\perp^2)$}
\label{App:basis-g1}

For the helicity PDF $g_1^a(x)=\int d^2k_\perp\,g_1^a(x,k_\perp^2)\equiv 
\int d^2k_\perp\,g_{1L}^a(x,k_\perp^2)$ we use in this work the leading-order 
parameterizations from \cite{Gluck:1998xa}.
If not otherwise stated the parametrizations are taken at the scale 
$Q^2=2.5\,{\rm GeV}^2$.

In lack of phenomenological information on the $k_\perp$-dependence of
$g_1^a(x,k_\perp^2)$ we explore lattice QCD results from \cite{Hagler:2009mb}
to constrain the Gaussian width in Eq.~(\ref{eq:g1}). 
On a lattice with pion and nucleon masses 
$m_\pi\approx 500\,{\rm MeV}$ and $M_N=1.291(23)\,{\rm GeV}$ 
and with an axial coupling constant $g_A^{(3)}= 1.209(36)$ reasonably
close to its physical value $1.2695(29)$ the following results were
obtained for the mean square transverse parton momenta \cite{Hagler:2009mb}.
For the unpolarized TMDs it was found
$\langle \kperp^2 \rangle_{f_1^u} = (0.3741\,{\rm GeV})^2$ and
$\langle \kperp^2 \rangle_{f_1^d} = (0.3839\,{\rm GeV})^2$.
For the helicity TMDs it was found
$\avkperp_{g_1^u} = (0.327\,{\rm GeV})^2$ and
$\avkperp_{g_1^d} = (0.385\,{\rm GeV})^2$. 
These values are quoted in Table~\ref{Table:Gauss-paramaters}.

@@

\ba
f_{1T}^{\perp q}(x,\kperp^2) =  f_{1T}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{f_{1T}^\perp}^2} e^{-\kperp^2/{\avkperp_{f_{1T}^\perp}}}
\label{sivers_new} \ .
\ea

@@

\newpage
\section{Convolution integrals and expressions in Gaussian Ansatz}
\label{App:factor}
